A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-11-15 documents/plm.tex
acks; figure 2

\acknowledgements
It is a pleasure to thank the whole \Kepler\ Team
  for designing, delivering, and operating a great facility,
  and for making all of the data public, in all its rawest forms, through the MAST interface.
We are also pleased to thank
  Ruth~Angus (Oxford),
  Bekki~Dawson (Berkeley),
  Michael~Hirsch (UCL),
  Dustin~Lang (CMU),
  Benjamin~T.~Montet (Caltech),
  David~Schiminovich (Columbia),
  and
  Jake Vanderplas (UW)
for valuable discussions, input, encouragement, and advice.

@@

>>>>

\acknowledgements
It is a pleasure to thank the whole \Kepler\ Team
  for designing, delivering, and operating a great facility,
  and for making all of the data public, in all its rawest forms, through the MAST interface.
We are also pleased to thank
  Ruth~Angus (Oxford),
  Bekki~Dawson (Berkeley),
  Michael~Hirsch (UCL),
  Dustin~Lang (CMU),
  Benjamin~T.~Montet (Caltech),
  David~Schiminovich (Columbia),
  and
  Jake Vanderplas (UW)
for valuable discussions, input, encouragement, and advice.
This project was partially supported by NSF grant IIS-1124794 and NASA grant NNX12AI50G.
This research made use of the NASA Astrophysics Data System.

@@

\clearpage
\begin{figure}
~ % DFM: replace this ~ with a figure
\caption{One quarter of photometric data for star XXX.
  The top panel shows the \Kepler\ SAP photometry.
  The next panel shows the \Kepler\ PDC photometry.
  The next shows the PDC photometry.
  The bottom panel shows the power spectra of the three lightcurves.\label{fig:example1}}
\end{figure}
